Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems

### 2018-04-18 LaTeX/main_revised.tex
almost done sallys comments to weak linkage

\noindent\textit{Conclusion 1C:}
\textbf{

}
\vspace{0.5cm}

>>>>

\noindent\textit{Conclusion 1C:}
\textbf{
Haploid selection allows trans-GSD transitions that weaken sex-linkage ($r<R\leq1/2$; potentially even shifting sex determination to a different chromosome) even when selection is sexually-antagonistic with directional selection in each diploid sex.  
With initially tight linkage, these transitions equalize the sex ratio by reducing linkage to alleles under haploid selection.
}
\vspace{0.5cm}
